---
title: "Data description: Aggregate behavior"
author: "Erik Ø. Sørensen"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(here)
#library(tidyverse)
mmzame_decisions = readRDS(here("data", "mmzame_decisions.rds"))
background = readRDS(here("data", "background.rds"))
```

This is to calculate the descriptives in the subsection on aggregate behavior in 
"Linking Social and Personal Preferences: Theory and Experiment" by William R. Zame, 
Bertil Tungodden, Erik Ø. Sørensen, Shachar Kariv, and Alexander W. Cappelen. 

Prepping of data is outlined in the drake file "plan.R". 

# Distribution of choices in the *Social Choice* treatment

Calculating the averages of $y/(x+y)$ in the social treatment, for all individuals,
and 
```{r}
average_social_decisions <- mmzame_decisions %>% 
  filter(treatment=="dictator") %>%
  mutate(yshare = y/(y+x)) %>%
  group_by(id) %>%
  summarize(mean_yshare = mean(yshare)) %>%
  mutate(selfish = (mean_yshare>0.95),
         impartial = (abs(mean_yshare - 0.5)<0.05))
```

Now, we can count the different types:
```{r}
(type_table <- average_social_decisions %>% 
  with(table(selfish,impartial)))
type_table / sum(type_table)
```

How many were even more selfless? 
```{r}
average_social_decisions %>% filter(mean_yshare<0.45) %>%
  arrange(mean_yshare)
```

Finally, we want a histogram of the mean share to the y-good:
```{r}
average_social_decisions %>% ggplot(aes(x=mean_yshare, y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  geom_histogram(binwidth=0.05, boundary=0) +
  labs(x = "Mean y/(x+y)",
       y = "Fraction",
       caption ="Decisions in the Social Choice treatment.") +
  theme_bw()
ggsave(here::here("graphs", "aggregate_social_choice.pdf"))
```
# Distribution of choices in the *Personal Risk* and the *Social Risk* treatments

In the personal risk and social risk treatments, it is not the average share
to the y-axis that is of importance, but the average share to the cheapest asset.
I also merge in the type classification based on social choices.

I rename treatments for the graph creation

```{r}
average_symmetric_decisions <- mmzame_decisions %>% 
  filter(treatment %in% c("moral", "risk")) %>%
  mutate(share_cheapest = if_else(maxy>maxx, y/(y+x), x/(y+x))) %>%
  group_by(treatment, id) %>%
  summarize(mean_cheapest = mean(share_cheapest)) %>%
  left_join(average_social_decisions, by="id") %>%
  ungroup() %>%
  mutate(treatmentf = fct_recode(factor(treatment, levels=c("risk","moral")),
         "Personal Risk" = "risk",
         "Social Risk" = "moral"))
```

Faceted histogram:
```{r}
average_symmetric_decisions %>% ggplot(aes(x=mean_cheapest, y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) +
  geom_histogram(binwidth=0.05, boundary=0.0) + 
  labs(x = "Mean share of cheapest asset in portfolio",
       y = "Fraction") +
  theme_bw() + facet_grid(.~treatmentf)
ggsave(here::here("graphs", "aggregate_risks.pdf"))
```

How may are in the extreme groups? 
```{r}
average_symmetric_decisions %>%
  mutate(more_than_95p = (mean_cheapest > 0.95),
         less_than_55p = (mean_cheapest < 0.55)) %>% 
  group_by(treatmentf, more_than_95p, less_than_55p) %>%
  summarize(n = n()) %>% knitr::kable()
```

