---
title: "Data description: Aggregate behavior"
author: "Erik Ø. Sørensen"
date: '`r format(Sys.time(), "%d %B, %Y")`'
html_document:
  keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(targets)
tar_load(mmzame_decisions, store = here::here("_targets"))
```

This is to calculate the descriptives in the subsection on aggregate behavior in 
"Linking Social and Personal Preferences: Theory and Experiment" by William R. Zame, 
Bertil Tungodden, Erik Ø. Sørensen, Shachar Kariv, and Alexander W. Cappelen. 

# Distribution of choices in the *Social Choice* treatment

Calculating the averages of $y/(x+y)$ in the social treatment, for all individuals,
and 
```{r}
average_social_decisions <- mmzame_decisions %>% 
  filter(treatment=="dictator") %>%
  mutate(yshare = y/(y+x)) %>%
  group_by(id) %>%
  summarize(mean_yshare = mean(yshare)) %>%
  mutate(selfish = (mean_yshare>0.95),
         impartial = (abs(mean_yshare - 0.5)<0.05))
```

Now, we can count the different types:
```{r}
(type_table <- average_social_decisions %>% 
  with(table(selfish,impartial)))
type_table / sum(type_table)
```

How many were even more selfless? 
```{r}
average_social_decisions %>% filter(mean_yshare<0.5) %>%
  arrange(mean_yshare)
```


```{r}
average_symmetric_decisions <- mmzame_decisions %>% 
  filter(treatment %in% c("moral", "risk")) %>%
  mutate(share_cheapest = if_else(maxy>maxx, y/(y+x), x/(y+x))) %>%
  group_by(treatment, id) %>%
  summarize(mean_cheapest = mean(share_cheapest)) %>%
  left_join(average_social_decisions, by="id") %>%
  ungroup() %>%
  mutate(treatmentf = fct_recode(factor(treatment, levels=c("risk","moral")),
         "Personal Risk" = "risk",
         "Social Risk" = "moral"))
```


How many are in the extreme groups? 
```{r}
average_symmetric_decisions %>%
  mutate(more_than_95p = (mean_cheapest > 0.95),
         less_than_55p = (mean_cheapest < 0.55),
         less_than_50p = (mean_cheapest < 0.5)) %>% 
  group_by(treatmentf, more_than_95p, less_than_55p, less_than_50p) %>%
  summarize(n = n()) %>% gt::gt()
```


```{r}
average_symmetric_decisions |> filter(mean_cheapest<0.5) |> gt::gt()
```

# Variant graph with all treatments

We want a bar-graph with grouped levels of the outcomes of the outcomes
in the two previous graphs. First I put the data all together in one dataframe
and normalize the names
```{r}
bar_data <- average_social_decisions %>% 
  bind_rows(average_symmetric_decisions) %>%
  mutate( treatment = if_else(is.na(treatment), "social", treatment)) %>%
  mutate(treatmentf = fct_recode(factor(treatment, levels=c("social", "risk","moral")),
                                 "Social Choice" = "social",
                                 "Personal Risk" = "risk",
                                 "Social Risk" = "moral")) %>%
  mutate( yshare = if_else(treatment=="social", mean_yshare, mean_cheapest)) %>%
  dplyr::select(id, treatmentf, yshare)
```

Having created the dataset, we now want to print a bar chart with grouped categories. We
need to group the outcome, `yshare`, into groups---we can use `cut`.

```{r}
bar_data <- bar_data %>% mutate(ygroup = cut_width(yshare, 0.10, boundary=1, closed="right"))
```
We want to present fractions at each group---and since we want `ggplot` to make room
for the zero-height bars, we do the counting and the completion ourselves
```{r}

bar_fractions <- bar_data %>% 
  group_by(treatmentf, ygroup) %>% 
  tally() %>%  
  ungroup() %>%
  complete(treatmentf,ygroup, fill=list(n=0)) %>%
  group_by(treatmentf) %>%
  mutate( fraction = n/sum(n))
```



Now, it should be possible to use ggplot to figure out how to present the groups:
```{r}
bar_fractions %>% ggplot(aes(x=ygroup, y=fraction, group=treatmentf, fill=treatmentf)) + 
  geom_bar(stat="identity", position=position_dodge2()) +
  labs(x = "Token shares",
       y = "Fraction of subjects") +
  theme_minimal() + 
  theme(legend.title=element_blank()) + 
  scale_fill_grey() +
  scale_y_continuous(breaks = c(0, 0.05, 0.1, 0.15,0.2,0.25,0.3,0.35,0.4,0.45,0.5))
ggsave(here::here("graphs","aggregate_choices.pdf"), width = 16, height = 10, units = "cm")
```


