---
title: "Long table with different group classifications"
author: "Erik Ø. Sørensen"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library("targets")
library("tidyverse")
library("revealedPrefs")
library("gt")
tar_load(mmzame_decisions, store = here::here("_targets"))
tar_load(all, store = here::here("_targets"))
```


# Creating main table of results

The construction of the input data is pushed into the *target* `all`. What
is needed is to present this in the shape we want.

Now, trying to put together a table with the outputs. I want to piece it 
together by groups of 4 columns (with optional counts), conditional on 
a partition of individuals, and conditional on a significance level. I also 
want to have an optional "header" column with number of observations.


## Code for constructing table of numbers
The construction is such that at the bottom level, `main_section` creates
a short collection of cells, `main_row` collects a number of sections
into a row, and `main_rows` creates all the necessary rows. 


```{r}
main_section <- function(df, partition, alpha, ns=FALSE,
                         cnames = c("p_SRISK = PRISK", "p_SRISK = SOCIAL", "p_SOCIAL = PRISK", "p_ALL DOMAINS")) {
  pvar <- sym(partition)
  content <- df |> dplyr::select(c(!!pvar, cnames)) |>
    group_by(!!pvar) |>
    summarize_at(vars(-group_cols()), function(x) { mean(x < alpha) }) |>
    arrange(-!!pvar) |>
    select(-!!pvar) |> as.matrix()
  if (ns) {
    n0 <- df |> filter(!!pvar==0) |> count() |> as.numeric()
    n1 <- df |> filter(!!pvar==1) |> count() |> as.numeric()
    nm <- as.matrix(c(n1,n0), nrow=2, ncol=1)
    content <- cbind(nm, content)
  }
  content
}
```


A full (two-row) line of data consists in three calls (for different significance levels) of this.

```{r}
main_row <- function(df, partition, cnames = c("p_SRISK = PRISK", "p_SRISK = SOCIAL", "p_SOCIAL = PRISK", "p_ALL DOMAINS")) {
  m1 <- main_section(df, partition, 0.01, ns=TRUE, cnames=cnames) |> as.data.frame()
  m2 <- main_section(df, partition, 0.05, cnames=cnames) |> as.data.frame()
  m3 <- main_section(df, partition, 0.1, cnames=cnames) |> as.data.frame()
  colnames(m1) <- c("n","p1_1","p2_1","p3_1","p4_1")
  colnames(m2) <- c("p1_5","p2_5","p3_5","p4_5")
  colnames(m3) <- c("p1_10","p2_10","p3_10","p4_10")
  cbind(m1,m2,m3)
}
```

Now, a table can be made for a vector of partitions:
```{r}
repeat_with_empty <- function(v) {
  new_v <- character(length(v) * 2)  # Create a character vector of double length, initialized with empty strings
  new_v[seq(1, length(new_v), by = 2)] <- v  # Assign original elements to every other position
  return(new_v)
}
main_rows <- function(df, partitions, cnames = c("p_SRISK = PRISK", "p_SRISK = SOCIAL", "p_SOCIAL = PRISK", "p_ALL DOMAINS")) {
  myf <- function(p) { main_row(df, p, cnames=cnames) }
  newdf <- purrr::map_dfr(partitions, myf) 
  cbind(repeat_with_empty(partitions), newdf)
}
```

Create all the numerical rows:

```{r}
ps <- c("selfish99","selfish975","selfish95","selfish90", "impartial05",
        "stochastic_symmetricd10","stochastic_symmetricd05","stochastic_symmetricd01")
all_numrows <- main_rows(all, ps)
```

Now, create numerical rows for alternative tests that *impose* symmetry.

```{r}
psm <- c("impartial05","stochastic_symmetricd10","stochastic_symmetricd05",
         "stochastic_symmetricd01")
all_numrows_with_symmetry <- main_rows(all,
                                       c("impartial05","stochastic_symmetricd10",
                                         "stochastic_symmetricd05","stochastic_symmetricd01"),
                                       cnames = c("p_mSRISK = mPRISK", "p_mSRISK = mSOCIAL", 
                                                  "p_mSOCIAL = mPRISK", "p_mALL DOMAINS"))
```



## Code for presenting the final results

First for the main (big) table in the paper:

```{r echo=FALSE}
tbl <- all_numrows |> 
  gt() |>
  fmt_number(columns = 3:14,
             decimals = 3) |>
    tab_spanner(
    label = "1% significance level",
    columns = 3:6
  ) |>
  tab_spanner(
    label = "5% significance level",
    columns = 7:10
  ) |>
  tab_spanner(
    label = "10% significance level",
    columns = 11:14
  ) |>
    cols_add(
    EmptyCol1 = "",
    .before = p1_1) |>
  cols_add( EmptyCol2 = "",
            .before = p1_5) |>
  cols_add( EmptyCol3 = "",
            .before = p1_10) |>
    cols_width(
      vars(EmptyCol1, EmptyCol2, EmptyCol3) ~ px(20)  # Set the width for the empty columns
    ) |>
  cols_label(
    `repeat_with_empty(partitions)` = "Partition",
    p1_1 = "(1)",
    p2_1 = "(2)",
    p3_1 = "(3)",
    p4_1 = "(4)",
    p1_5 = "(1)",
    p2_5 = "(2)",
    p3_5 = "(3)",
    p4_5 = "(4)",
    p1_10 = "(1)",
    p2_10 = "(2)",
    p3_10 = "(3)",
    p4_10 = "(4)",
    EmptyCol1 = "",
    EmptyCol2 = "",
    EmptyCol3 = ""
    ) |>
  tab_style(
    style = list(
      cell_text(weight="bold")
    ),
    locations = cells_body(
      columns = c(4,9,14),
      rows = c(1,3,5,7)
    )
  ) |>
    tab_style(
    style = list(
      cell_text(weight="bold")
    ),
    locations = cells_body(
      columns = c(5,10,15),
      rows = c(9,11,13,15)
    )
  )
tbl
tbl |> gtsave(filename = here::here("tables", "main_table.tex"), to = "latex")
```

Now for the variant of panel B that impose symmetry (for the appendix):


```{r echo=FALSE}
tblC <- all_numrows_with_symmetry |> 
  gt() |>
  fmt_number(columns = 3:14,
             decimals = 3) |>
    tab_spanner(
    label = "1% significance level",
    columns = 3:6
  ) |>
  tab_spanner(
    label = "5% significance level",
    columns = 7:10
  ) |>
  tab_spanner(
    label = "10% significance level",
    columns = 11:14
  ) |>
    cols_add(
    EmptyCol1 = "",
    .before = p1_1) |>
  cols_add( EmptyCol2 = "",
            .before = p1_5) |>
  cols_add( EmptyCol3 = "",
            .before = p1_10) |>
    cols_width(
      vars(EmptyCol1, EmptyCol2, EmptyCol3) ~ px(20)  # Set the width for the empty columns
    ) |>
  cols_label(
    `repeat_with_empty(partitions)` = "Partition",
    p1_1 = "(1)",
    p2_1 = "(2)",
    p3_1 = "(3)",
    p4_1 = "(4)",
    p1_5 = "(1)",
    p2_5 = "(2)",
    p3_5 = "(3)",
    p4_5 = "(4)",
    p1_10 = "(1)",
    p2_10 = "(2)",
    p3_10 = "(3)",
    p4_10 = "(4)",
    EmptyCol1 = "",
    EmptyCol2 = "",
    EmptyCol3 = ""
    ) |>
  tab_style(
    style = list(
      cell_text(weight="bold")
    ),
    locations = cells_body(
      columns = c(5,10,15),
      rows = c(1,3,5,7)
    )
  )
tblC
tblC |> gtsave(filename = here::here("tables", "main_tableC.tex"), to = "latex")
```




# Matching of different impartial definitions

There are more impartial/symmetric individuals with the stochastic tests. 
A Venn-diagram with 4 groups is a mess to look at. But there are alternatives,
let's look at the size of all non-empty intersections:

```{r}
classifications <- all |> 
  select(c("impartial05", "stochastic_symmetricd01", "stochastic_symmetricd05", "stochastic_symmetricd10")) |>
  rename(`Tokenshare between 0.45 and 0.55` = impartial05,
         "Stochastic symmmetry test with alpha=0.01" = stochastic_symmetricd01,
          "Stochastic symmmetry test with alpha=0.05" = stochastic_symmetricd05,
          "Stochastic symmmetry test with alpha=0.10" = stochastic_symmetricd10) |>
  data.frame() 
intersections <- UpSetR::upset(classifications, order.by="freq") 
intersections

pdf(file = here::here("graphs","impartial_definition_intersections.pdf"), onefile=FALSE, width = 6.3, height = 3.93)
print(intersections)
dev.off()
```

