---
title: "Long table with different group classifications"
author: "Erik Ø. Sørensen"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library("targets")
library("tidyverse")
library("revealedPrefs")
tar_load(mmzame_decisions)
tar_load(p3_00)
tar_load(p4_00)
tar_load(p2_00)
tar_load(pall_domains)
tar_load(symmetricp_dict)
tar_load(sym_dict)
```


## Extracting all p-values from everyone

```{r}
p_from_list <- function(x) {
  data.frame(id = x$id, p = x$p_com)
}
allp3 <- map(p3_00, p_from_list) |> bind_rows() |> mutate(tst="SRISK = PRISK")
allp4 <- map(p4_00, p_from_list) |> bind_rows() |> mutate(tst="SRISK = SOCIAL")
allp2 <- map(p2_00, p_from_list) |> bind_rows() |> mutate(tst="SOCIAL = PRISK")
alld <- map(pall_domains, p_from_list) |> bind_rows() |> mutate(tst="ALL DOMAINS")

p_values <- list(allp3, allp4, allp2, alld) |> 
  bind_rows()  |>
  mutate(reject = as.numeric(p<0.05)) |>
  pivot_wider(id_cols="id", names_from="tst", values_from=c(p,reject))
```


## Different categorizations

```{r}
shares <- mmzame_decisions |> 
  filter(treatment=="dictator") |>
  group_by(id) |>
  summarize( mean_self = mean(y/(y+x))) |>
  mutate(selfish975 = as.numeric(mean_self>0.975),
         selfish95 = as.numeric(mean_self>0.95),
         selfish90 = as.numeric(mean_self>0.90),
         impartial05 = as.numeric( abs(mean_self - 0.5) < 0.05),
         impartial10 = as.numeric( abs(mean_self - 0.5) < 0.10)) 
```


We have the statistical test of symmetry in the social risk domain.

```{r}
stochastic_symmetric <- map(symmetricp_dict, function(x) { data.frame( id = x$id, p=x$p)}) |> 
  bind_rows() |> 
  mutate(stochastic_symmetricp = p,
         stochastic_symmetricd05 = as.numeric(p>0.05),
         stochastic_symmetricd01 = as.numeric(p>0.01),
         stochastic_symmetricd10 = as.numeric(p>0.10)) |>
  select(c(id, stochastic_symmetricp, stochastic_symmetricd01, stochastic_symmetricd05, stochastic_symmetricd10))
```

A new way of classification is a non-stochastic variant of the symmetry test.
First, calculate CCEI on the original data (n=50). Then concatenate this with the
symmetric data, for a total of n=100. Run the CCEI on the long data, which will
not be larger than the short CCEI. If the long CCEI / short CCEI > 0.95 
(Varian's cutoff), we say that there is symmetry. 


```{r}
CCEI_nonstochastic <- purrr::map(sym_dict, p_symmetric_nonstochastic) |> 
  bind_rows() |>
  mutate(CCEI_nonstochastic_sym95 = as.numeric( (sym_long / sym_short)>0.95),
         CCEI_nonstochastic_sym90 = as.numeric( (sym_long / sym_short)>0.90)) |>
  select(c(id, CCEI_nonstochastic_sym90, CCEI_nonstochastic_sym95))
```



## Putting things together

```{r}
all <- shares |> 
  left_join(p_values) |> 
  left_join(stochastic_symmetric) |>
  left_join(CCEI_nonstochastic) |>
  select( c("id",
            "selfish95","selfish90",
            "impartial05","impartial10",
            "stochastic_symmetricd01", "stochastic_symmetricd05", "stochastic_symmetricd10",
            "CCEI_nonstochastic_sym90", "CCEI_nonstochastic_sym95",
            "reject_SRISK = PRISK", "reject_SRISK = SOCIAL", "reject_SOCIAL = PRISK", "reject_ALL DOMAINS",
            "p_SRISK = PRISK", "p_SRISK = SOCIAL", "p_SOCIAL = PRISK", "p_ALL DOMAINS"))
```

Outputting to a spreadsheet:

```{r}
write_excel_csv(all, here::here("tables", "longtable.csv"))
```





