---
title: "Long table with different group classifications"
author: "Erik Ø. Sørensen"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library("targets")
library("tidyverse")
library("revealedPrefs")
library("gt")
tar_load(mmzame_decisions, store = here::here("_targets"))
tar_load(p3_00, store = here::here("_targets"))
tar_load(p4_00, store = here::here("_targets"))
tar_load(p2_00, store = here::here("_targets"))
tar_load(pall_domains, store = here::here("_targets"))
tar_load(symmetricp_dict, store = here::here("_targets"))
tar_load(sym_dict, store = here::here("_targets"))
```


## Extracting all p-values from everyone

```{r}
p_from_list <- function(x) {
  data.frame(id = x$id, p = x$p_com)
}
allp3 <- map(p3_00, p_from_list) |> bind_rows() |> mutate(tst="SRISK = PRISK")
allp4 <- map(p4_00, p_from_list) |> bind_rows() |> mutate(tst="SRISK = SOCIAL")
allp2 <- map(p2_00, p_from_list) |> bind_rows() |> mutate(tst="SOCIAL = PRISK")
alld <- map(pall_domains, p_from_list) |> bind_rows() |> mutate(tst="ALL DOMAINS")

p_values <- list(allp3, allp4, allp2, alld) |> 
  bind_rows()  |>
  mutate(reject = as.numeric(p<0.05)) |>
  pivot_wider(id_cols="id", names_from="tst", values_from=c(p,reject))
```


## Different categorizations

```{r}
shares <- mmzame_decisions |> 
  filter(treatment=="dictator") |>
  group_by(id) |>
  summarize( mean_self = mean(y/(y+x))) |>
  mutate(selfish99 = as.numeric(mean_self>0.99),
         selfish975 = as.numeric(mean_self>0.975),
         selfish95 = as.numeric(mean_self>0.95),
         selfish90 = as.numeric(mean_self>0.90),
         selfish75 = as.numeric(mean_self>0.75),
         impartial05 = as.numeric( abs(mean_self - 0.5) < 0.05),
         impartial10 = as.numeric( abs(mean_self - 0.5) < 0.10)) 
```


We have the statistical test of symmetry in the social risk domain.

```{r}
stochastic_symmetric <- map(symmetricp_dict, function(x) { data.frame( id = x$id, p=x$p)}) |> 
  bind_rows() |> 
  mutate(stochastic_symmetricp = p,
         stochastic_symmetricd05 = as.numeric(p>0.05),
         stochastic_symmetricd01 = as.numeric(p>0.01),
         stochastic_symmetricd10 = as.numeric(p>0.10)) |>
  select(c(id, stochastic_symmetricp, stochastic_symmetricd01, stochastic_symmetricd05, stochastic_symmetricd10))
```

A new way of classification is a non-stochastic variant of the symmetry test.
First, calculate CCEI on the original data (n=50). Then concatenate this with the
symmetric data, for a total of n=100. Run the CCEI on the long data, which will
not be larger than the short CCEI. If the long CCEI / short CCEI > 0.95 
(Varian's cutoff), we say that there is symmetry. 


```{r}
CCEI_nonstochastic <- purrr::map(sym_dict, p_symmetric_nonstochastic) |> 
  bind_rows() |>
  mutate(CCEI_nonstochastic_sym95 = as.numeric( (sym_long / sym_short)>0.95),
         CCEI_nonstochastic_sym90 = as.numeric( (sym_long / sym_short)>0.90)) |>
  select(c(id, CCEI_nonstochastic_sym90, CCEI_nonstochastic_sym95))
```



## Putting things together

```{r}
all <- shares |> 
  left_join(p_values) |> 
  left_join(stochastic_symmetric) |>
  left_join(CCEI_nonstochastic) |>
  select( c("id",
            "selfish99", "selfish975","selfish95","selfish90","selfish75",
            "impartial05","impartial10",
            "stochastic_symmetricd01", "stochastic_symmetricd05", "stochastic_symmetricd10",
            "CCEI_nonstochastic_sym90", "CCEI_nonstochastic_sym95",
            "reject_SRISK = PRISK", "reject_SRISK = SOCIAL", "reject_SOCIAL = PRISK", "reject_ALL DOMAINS",
            "p_SRISK = PRISK", "p_SRISK = SOCIAL", "p_SOCIAL = PRISK", "p_ALL DOMAINS"))
```

Outputting to a spreadsheet:

```{r}
write_excel_csv(all, here::here("tables", "longtable.csv"))
```

Now, trying to put together a table with the outputs. I want to piece it 
together by groups of 4 columns (with optional counts), conditional on 
a partition of individuals, and conditional on a significance level. I also 
want to have an optional "header" column with number of observations.

```{r}
main_section <- function(df, partition, alpha, ns=FALSE) {
  pvar <- sym(partition)
  cnames <- c("p_SRISK = PRISK", "p_SRISK = SOCIAL", "p_SOCIAL = PRISK", "p_ALL DOMAINS")
  content <- df |> dplyr::select(c(!!pvar, cnames)) |>
    group_by(!!pvar) |>
    summarize_at(vars(-group_cols()), function(x) { mean(x < alpha) }) |>
    arrange(-!!pvar) |>
    select(-!!pvar) |> as.matrix()
  if (ns) {
    n0 <- df |> filter(!!pvar==0) |> count() |> as.numeric()
    n1 <- df |> filter(!!pvar==1) |> count() |> as.numeric()
    nm <- as.matrix(c(n1,n0), nrow=2, ncol=1)
    content <- cbind(nm, content)
  }
  content
}
```


A full (two-row) line of data consists in three calls (for different significance levels) of this.

```{r}
main_row <- function(df, partition) {
  m1 <- main_section(df, partition, 0.01, ns=TRUE) |> as.data.frame()
  m2 <- main_section(df, partition, 0.05) |> as.data.frame()
  m3 <- main_section(df, partition, 0.1) |> as.data.frame()
  colnames(m1) <- c("n","p1_1","p2_1","p3_1","p4_1")
  colnames(m2) <- c("p1_5","p2_5","p3_5","p4_5")
  colnames(m3) <- c("p1_10","p2_10","p3_10","p4_10")
  cbind(m1,m2,m3)
}
```

Now, a table can be made for a vector of partitions:
```{r}
repeat_with_empty <- function(v) {
  new_v <- character(length(v) * 2)  # Create a character vector of double length, initialized with empty strings
  new_v[seq(1, length(new_v), by = 2)] <- v  # Assign original elements to every other position
  return(new_v)
}
main_rows <- function(df, partitions) {
  myf <- function(p) { main_row(df, p) }
  newdf <- purrr::map_dfr(partitions, myf) 
  cbind(repeat_with_empty(partitions), newdf)
}
```

Create all the numerical rows:

```{r}
ps <- c("selfish99","selfish975","selfish95","selfish90", "impartial05","stochastic_symmetricd10","stochastic_symmetricd05","stochastic_symmetricd01")
all_numrows <- main_rows(all, ps)
```



## Creating the output table

```{r}
tbl <- all_numrows |> 
  gt() |>
  fmt_number(columns = 3:14,
             decimals = 3) |>
    tab_spanner(
    label = "1% significance level",
    columns = 3:6
  ) |>
  tab_spanner(
    label = "5% significance level",
    columns = 7:10
  ) |>
  tab_spanner(
    label = "10% significance level",
    columns = 11:14
  ) |>
  cols_label(
    `repeat_with_empty(partitions)` = "Partition",
    p1_1 = "(1)",
    p2_1 = "(2)",
    p3_1 = "(3)",
    p4_1 = "(4)",
    p1_5 = "(1)",
    p2_5 = "(2)",
    p3_5 = "(3)",
    p4_5 = "(4)",
    p1_10 = "(1)",
    p2_10 = "(2)",
    p3_10 = "(3)",
    p4_10 = "(4)"
    ) |>
  tab_style(
    style = list(
      cell_text(weight="bold")
    ),
    locations = cells_body(
      columns = c(3,7,11),
      rows = c(1,3,5,7)
    )
  ) |>
    tab_style(
    style = list(
      cell_text(weight="bold")
    ),
    locations = cells_body(
      columns = c(4,8,12),
      rows = c(9,11,13,15)
    )
  )
tbl
tbl |> gtsave(filename = here::here("tables", "main_table.tex"), to = "latex")
```



