---
title: "Appendix"
author: "Erik Ø. Sørensen"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    toc: true
    toc_depth: 2
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#source(here::here("packages.R"))
#source(here::here("functions.R"))
tar_load(mmzame_decisions, store = here::here("_targets"))
```

For section A2.2, we do an analysis of order effects.

The order we decided on for the 4 treatments was to always first run the "Social
Risk" treatment, and then the other 3 treatments in randomized order. So we have
data on the 3 treatments in 6 different sequences. We can use this to create a
test based on the share allocated to self in the "Social Choice" treatment (by
sequence) and similarly the share allocated to the cheapest asset in the
"Personal Risk" treatment.

```{r Creating data, message=FALSE, warning=FALSE, include=FALSE}
# To implement, first create a data set with the individual orders of treatments and
# join to decisions:
tar_load(mmzame_decisions_alltreatments, store = here::here("_targets"))
sequence <- mmzame_decisions_alltreatments %>% 
  filter(round==1) %>%
  pivot_wider(id_cols = id, names_from = treatment, values_from = phase, names_prefix = "seq_")
ordered_means <- mmzame_decisions_alltreatments %>% 
  left_join(sequence) %>% 
  mutate(DRO_order = paste(seq_dictator, seq_risk, seq_observer, sep=","), 
         share_self = y/(y+x),
         share_cheapest = if_else(maxy>maxx, y/(y+x), x/(y+x))) %>%
  group_by(id, DRO_order, treatment) %>%
  summarize(share_self = mean(share_self),
            share_cheapest = mean(share_cheapest)) %>%
  ungroup()
```
First for risk, we test 
the share allocated the cheapest asset by sequence. Note that two sequences, (SR, PR, SC, O) and (SR, PR, O, SC)
should be the same for the choices made in the PR domain, so reduce these to a single order for the
purpose of testing, there are 5 relevant orders.

```{r Testing order for Personal Risk, echo=FALSE}
ordered_means %>% 
  filter(treatment=="risk") |>
  mutate(R_order = ifelse(DRO_order %in% c("3,2,4","4,2,3"), "R2", DRO_order)) |>
  kruskal.test(share_cheapest ~ R_order, data=_)
```
Now for "Social Choice", we look at the share taken for self in SC, whether it depends on 
order. In this case, the sequences (SR, SC, PR, O) and (SR, SC, O, PR) should also 
be treated as equivalent.
```{r Testing order for Social Choice, echo=FALSE}
ordered_means |> 
  filter(treatment=="dictator") |>
  mutate(D_order = ifelse(DRO_order %in% c("2,3,4","2,4,3"), "D2", DRO_order)) |>
  kruskal.test(share_self ~ D_order, data=_) 
```
And for the observer choice itself (not used in the paper). In this case,
the sequences (SR, O, SC, PR) and (SR, O, PR, SC) should be treated as
equivalent.
```{r Testing order for Observer, echo=FALSE}
ordered_means %>% filter(treatment=="observer") |>
  mutate(O_order = ifelse(DRO_order %in% c("3,4,2","4,3,2"), "O2", DRO_order)) |>
  kruskal.test(share_cheapest ~ O_order, data=_) 
```





