---
title: "Testing rationality"
author: "Erik Ø. Sørensen"
date: '`r format(Sys.time(), "%d %B, %Y")`'
html_document:
  keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(here)
#source(here("packages.R"))
#source(here("functions.R")) 
mmzame_decisions = readRDS(here("data", "mmzame_decisions.rds")) %>% 
  filter(treatment %in% c("moral", "risk", "dictator"))
background = readRDS(here("data", "background.rds"))
```

We are interested in Afriat's cost efficiency index for each of the treatments.

First, recoding to final treatment names, then calculating CCEI's for each 
individual/treatment combination.
```{r}
mmzame_decisions <- mmzame_decisions %>% 
  mutate(treatment = fct_recode(as_factor(treatment),
                                "Social Choice" = "dictator",
                                "Social Risk" = "moral",
                                "Personal Risk" = "risk"))
cceis <- c()
domains <- c()
ids <- c()
for (i in unique(mmzame_decisions$id)) {
  for (j in unique(mmzame_decisions$treatment)) {
    x_df <- mmzame_decisions %>% filter(id==i, treatment==j) %>% select(x,y)
    p_df <- mmzame_decisions %>% filter(id==i, treatment==j) %>% mutate(px=maxy/maxx, py = 1) %>% select(px,py)
    ids <- c(ids, i)
    cceis <- c(cceis, ccei(x_df,p_df))
    domains <- c(domains, j)
  }
}
ccei_df <- tibble(id=ids, 
                  ccei=cceis, 
                  domain=factor(domains))
```

Now, some descriptive statics on these CCEIs:
```{r}
ccei_df %>% group_by(domain) %>%
  summarize( mean_ccei = mean(ccei),
             above_90 = mean( ccei>0.9)) %>%
  knitr::kable(digits=3)
```

I have pre-calculated the Bronars numbers, and summarize these:
```{r}
loadd("pure_bronars")
bronars_df <- tibble(domain = "Bronars", ccei=pure_bronars)
bronars_df %>% summarize(Bronars_mean_ccei = mean(ccei),
                         Bronars_above_90 = mean( ccei>0.9)) %>%
  knitr::kable(digits=3)
```

I append the Bronars data to the actual CCEIs and create a faceted histogram:

```{r}
ccei_df %>% mutate(domain = as.character(domain)) %>%
  bind_rows(bronars_df) %>%
  mutate(domain = factor(domain, levels=c("Social Choice", 
                                          "Personal Risk", 
                                          "Social Risk",
                                          "Bronars"))) %>%
  ggplot(aes(x=ccei, y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) +
  geom_histogram(binwidth=0.05, boundary=0) + 
  theme_bw() + 
  labs(x="CCEI", y="Fraction",
       caption="Afriat's Cost Efficiency Index (CCEI) for each of the three experimental\ntreatments and for 25 000 simulated draws of individuals with uniform random behavior. ") +
  facet_wrap(.~domain) 
ggsave(here("graphs", "empirical_cceis_and_Bronars.pdf"))
```

