---
title: "Testing the Theory"
author: "Erik Ø. Sørensen"
date: '`r format(Sys.time(), "%d %B, %Y")`'
html_document:
  keep_md: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
library(targets)
knitr::opts_chunk$set(echo = TRUE)
tar_load(mmzame_decisions, store = here::here("_targets"))
```

This is to present the tests on individual behavior in 
**"Linking Social and Personal Preferences: Theory and Experiment"** by William R. Zame, 
Bertil Tungodden, Erik Ø. Sørensen, Shachar Kariv, and Alexander W. Cappelen. 

Prepping of data and pre-calculation of test statistics is outlined in the drake file "_targets.R". 

```{r}
tar_load("p3_00", store = here::here("_targets"))
tar_load("p3_05", store = here::here("_targets"))
tar_load("p3_10", store = here::here("_targets"))
tar_load("p3_15", store = here::here("_targets"))
tar_load("p3_20", store = here::here("_targets"))
tar_load("p4_00", store = here::here("_targets"))
tar_load("p4_05", store = here::here("_targets"))
tar_load("p4_10", store = here::here("_targets"))
tar_load("p4_15", store = here::here("_targets"))
tar_load("p4_20", store = here::here("_targets"))
tar_load("selfish", store = here::here("_targets"))
tar_load("symmetric", store = here::here("_targets"))
```

# Testing proposition selfish
Creating all the graphs for testing selfish proposition:
```{r}
graph_list <- list()
obs_list3 <- list()
for (x in p3_00) {
  if (!(x$id %in% selfish$id))
    next
  df3 <- tibble(cceis=x$cceis_permuted)
  obs_list3[[x$id]] <- tibble(id = x$id,
                              p_min = x$p_min,
                              p_max = x$p_max,
                              p_com = x$p_com)
  caption <- paste0("Id=", x$id,". ")
  caption <- paste0(caption, "p(min)=", format(x$p_min,  digits=3), ", p(max)=", 
                    format(x$p_max, digits=3), ", combined p=", format(x$p_com, digits=3),".")
  g <- df3 %>% 
    ggplot(aes(x=cceis, y= (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
    geom_histogram(binwidth = 0.01, boundary=0) + 
    xlim(-0.01,1.01) + 
    geom_vline(xintercept = x$ccei1) +
    geom_vline(xintercept = x$ccei2) + 
    theme_minimal() +
    labs(x = "Afriat's CCEI", y = "Fraction", caption = caption) +
    scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0))
  graph_list[[x$id]] <- g
  fname <- paste0("prop3_id_", x$id,".pdf")
#  ggsave(here("graphs", "prop3_tests", fname), 
#         plot = g, width=7.29, height = 4.5, units="in")
}
```

Making a 4-panel version for the main paper. 
```{r message=FALSE, warning=FALSE}
p3A <- graph_list[[505]] + xlim(0.65,1) + 
  theme(plot.caption=element_blank()) + labs(x="CCEI", y="Fraction of permutations")
p3B <- graph_list[[729]] + xlim(0.65,1) + 
  theme(plot.caption=element_blank()) + labs(x="CCEI", y="Fraction of permutations")
p3C <- graph_list[[514]] + xlim(0.65,1) + 
  theme(plot.caption=element_blank()) + labs(x="CCEI", y="Fraction of permutations")
p3D <- graph_list[[502]] + xlim(0.65,1) + 
  theme(plot.caption=element_blank()) + labs(x="CCEI", y="Fraction of permutations")
p3_joint <- p3A + p3B + p3C + p3D + plot_annotation(tag_levels = 'A') 
p3_joint
ggsave(here::here("graphs","prop3_permutations.pdf"), plot=p3_joint, 
       width=7.29, height = 4.5, units="in")
#embed_fonts(here::here("graphs","prop3_permutations.pdf"))
```

What are the numbers?


```{r}
prop3 <- bind_rows( obs_list3)
prop3 %>% mutate(sign10 = p_com<0.1,
                 sign05 = p_com<0.05,
                 sign01 = p_com<0.01) %>%
  summarize(n_sign10 = sum(sign10),
            n_sign05 = sum(sign05),
            n_sign01 = sum(sign01))
```


For the people we show in the graph:
```{r}
prop3 |> filter(id %in% c(511,635,317,645)) |> gt::gt() |> gt::fmt_number(decimals = 3, columns = 2:4)
```



# Testing impartial proposition 
The same graphs for testing impartial proposition is available, but intended for an online appendix only.

```{r}
graph_list <- list()
obs_list4 <- list()
for (x in p4_00) {
  if (!(x$id %in% symmetric$id))
    next
  df <- tibble(cceis=x$cceis_permuted)
  obs_list4[[x$id]] <- tibble(id = x$id,
                              p_min = x$p_min,
                              p_max = x$p_max,
                              p_com = x$p_com)
  caption <- paste0("Id=", x$id,". ")
  caption <- paste0(caption, "p(min)=", format(x$p_min,  digits=3), ", p(max)=", 
                    format(x$p_max, digits=3), ", combined p=", format(x$p_com, digits=3),".")
  g <- df %>% 
    ggplot(aes(x=cceis, y= (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
    geom_histogram(binwidth = 0.01, boundary=0) + 
    xlim(-0.01,1.01) + 
    geom_vline(xintercept = x$ccei1) +
    geom_vline(xintercept = x$ccei2) + 
    theme_minimal() +
    labs(x = "Afriat's CCEI", y = "Fraction", caption = caption)
  graph_list[[x$id]] <- g
  fname <- paste0("prop4_id_", x$id,".pdf")
#  ggsave(here("graphs", "prop4_tests", fname), 
#         plot = g, width=7.29, height = 4.5, units="in")
}
```

What are the numbers?


```{r}
prop4 <- bind_rows( obs_list4)
prop4 %>% mutate(sign10 = p_com<0.1,
                 sign05 = p_com<0.05,
                 sign01 = p_com<0.01) %>%
  summarize(n_sign10 = sum(sign10),
            n_sign05 = sum(sign05),
            n_sign01 = sum(sign01)) |> gt::gt()
```




# Creating graph to showcase the power of the experiment.

We want to joint all the data from the simulations
```{r}
p3s <- c(p3_00, p3_05, p3_10, p3_15, p3_20) %>%
  keep(function(x) x$id %in% selfish$id) %>%
  map_df(function(x) tibble(p_bronars=x$p_Bronars, p_prop=x$p_com, prop="Proposition 3")) %>%
  bind_rows()
p4s <- c(p4_00, p4_05, p4_10, p4_15, p4_20) %>%
  keep(function(x) x$id %in% symmetric$id) %>%
  map_df(function(x) tibble(p_bronars=x$p_Bronars, p_prop=x$p_com, prop="Proposition 4")) %>%
  bind_rows()
```

We want a table variant, first for the selfish proposition:
```{r}
power_df <- p3s # %>% bind_rows(p4s)
power <- power_df %>%  mutate(significant_01 = (p_prop<0.01),
                              significant_05 = (p_prop<0.05),
                              significant_10 = (p_prop<0.10)) %>%
  pivot_longer(starts_with("significant_"), names_to="significance_level", 
               values_to = "significance") %>%
  group_by(p_bronars, significance_level) %>%
  summarize(significant_fraction = mean(significance)) %>%
  ungroup() %>%
  pivot_wider(names_from=p_bronars, names_prefix="mu=", 
              values_from=significant_fraction)
pwA <- power %>% gt::gt() |> gt::fmt_number(decimals=3) |>
  gt::tab_spanner(label = "Probability of random choice replacement", columns = 2:6) |>
  gt::tab_spanner(label = "Testing proposition 2 (selfish)", columns=1:6)
pwA
pwA |> gt::gtsave(filename = here::here("tables", "power_A.tex"), to = "latex")
```

Now also for the impartial proposition:

```{r}
power_df <- p4s 
power <- power_df %>%  mutate(significant_01 = (p_prop<0.01),
                              significant_05 = (p_prop<0.05),
                              significant_10 = (p_prop<0.10)) %>%
  pivot_longer(starts_with("significant_"), names_to="significance_level", 
               values_to = "significance") %>%
  group_by(p_bronars, significance_level) %>%
  summarize(significant_fraction = mean(significance)) %>%
  ungroup() %>%
  pivot_wider(names_from=p_bronars, names_prefix="mu=", 
              values_from=significant_fraction)
pwB <- power %>% gt::gt() |> gt::fmt_number(decimals=3) |>
  gt::tab_spanner(label = "Probability of random choice replacement", columns = 2:6) |>
  gt::tab_spanner(label = "Testing proposition 3 (impartial)", columns=1:6)
pwB
pwB |> gt::gtsave(filename = here::here("tables", "power_B.tex"), to = "latex")
```





