---
title: "Testing the Theory"
author: "Erik Ø. Sørensen"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(here)
#source(here("packages.R"))
#source(here("functions.R")) 
mmzame_decisions = readRDS(here("data", "mmzame_decisions.rds")) %>% 
  filter(treatment %in% c("moral", "risk", "dictator"))
background = readRDS(here("data", "background.rds"))
```

This is to present the tests on individual behavior in 
**"Linking Social and Personal Preferences: Theory and Experiment"** by William R. Zame, 
Bertil Tungodden, Erik Ø. Sørensen, Shachar Kariv, and Alexander W. Cappelen. 

Prepping of data and pre-calculation of test statistics is outlined in the drake file "plan.R". 

```{r}
loadd("p3_00")
loadd("p3_05")
loadd("p3_10")
loadd("p3_15")
loadd("p3_20")
loadd("p4_00")
loadd("p4_05")
loadd("p4_10")
loadd("p4_15")
loadd("p4_20")
loadd("selfish")
loadd("symmetric")
```

# Testing proposition 3
Creating all the graphs for testing proposition 3:
```{r}
graph_list <- list()
for (x in p3_00) {
  if (!(x$id %in% selfish$id))
    next
  df <- tibble(cceis=x$cceis_permuted)
  caption <- paste0("Id=", x$id,". ")
  caption <- paste0(caption, "p(min)=", format(x$p_min,  digits=3), ", p(max)=", 
                    format(x$p_max, digits=3), ", combined p=", format(x$p_com, digits=3),".")
  g <- df %>% 
    ggplot(aes(x=cceis, y= (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
    geom_histogram(binwidth = 0.01, boundary=0) + 
    xlim(-0.01,1.01) + 
    geom_vline(xintercept = x$ccei1) +
    geom_vline(xintercept = x$ccei2) + 
    theme_bw() +
    labs(x = "CCEI", y = "Fraction", caption = caption)
  graph_list[[x$id]] <- g
  fname <- paste0("prop3_id_", x$id,".pdf")
  ggsave(here("graphs", "prop3_tests", fname), 
         plot = g, width=7, height = 5, units="in")
}
```

Making a 4-panel version for the main paper. 
```{r message=FALSE, warning=FALSE}
p3A <- graph_list[[505]] + xlim(0.65,1)
p3B <- graph_list[[729]] + xlim(0.65,1)
p3C <- graph_list[[514]] + xlim(0.65,1)
p3D <- graph_list[[502]] + xlim(0.65,1)
p3_joint <- p3A + p3B + p3C + p3D + plot_annotation(tag_levels = 'A') 
p3_joint
ggsave(here("graphs","prop3_permutations.pdf"), plot=p3_joint, 
       width=7, height = 5, units="in")
```

# Testing proposition 4
The same graphs for testing proposition 4 is available, but intended for an online appendix only.

```{r}
graph_list <- list()
for (x in p4_00) {
  if (!(x$id %in% symmetric$id))
    next
  df <- tibble(cceis=x$cceis_permuted)
  caption <- paste0("Id=", x$id,". ")
  caption <- paste0(caption, "p(min)=", format(x$p_min,  digits=3), ", p(max)=", 
                    format(x$p_max, digits=3), ", combined p=", format(x$p_com, digits=3),".")
  g <- df %>% 
    ggplot(aes(x=cceis, y= (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
    geom_histogram(binwidth = 0.01, boundary=0) + 
    xlim(-0.01,1.01) + 
    geom_vline(xintercept = x$ccei1) +
    geom_vline(xintercept = x$ccei2) + 
    theme_bw() +
    labs(x = "CCEI", y = "Fraction", caption = caption)
  graph_list[[x$id]] <- g
  fname <- paste0("prop4_id_", x$id,".pdf")
  ggsave(here("graphs", "prop4_tests", fname), 
         plot = g, width=7, height = 5, units="in")
}
```

# Creating graph with final p-values

We want plots of p-values for the two propositions in the paper. 
Histograms of p-values from all the permutation tests from the relevant
tests.
```{r}
prop3_ps <- map_dbl( keep(p3_00, function(x) (x$id %in% selfish$id)),
                     function(x) x$p_com)
prop3_df <- tibble(p=prop3_ps)
prop4_ps <- map_dbl( keep(p4_00, function(x) (x$id %in% symmetric$id)),
                     function(x) x$p_com)
prop4_df <- tibble(p=prop4_ps)
prop3_h <- prop3_df %>% ggplot(aes(x=p, y= (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  geom_histogram(binwidth=0.05, boundary=0) +
  theme_bw() + 
  labs(x = "p-value",
       y = "Fraction",
       caption="Tests of Proposition 3 on the selfish individuals.")
prop4_h <- prop4_df %>% ggplot(aes(x=p, y= (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  geom_histogram(binwidth=0.05, boundary=0) +
  theme_bw() + 
  labs(x = "p-value",
       y = "Fraction",
       caption="Tests of Proposition 4 on the impartial individuals.")
propositions <- prop3_h + prop4_h + plot_annotation(tag_levels = 'A')
propositions
ggsave(here("graphs", "test_of_propositions.pdf"), plot=propositions, 
       width=7, height = 5, units="in")
```

# Creating graph to showcase the power of the experiment.

We want to joint all the data to from the simulations
```{r}
p3s <- c(p3_00, p3_05, p3_10, p3_15, p3_20) %>%
  keep(function(x) x$id %in% selfish$id) %>%
  map_df(function(x) tibble(p_bronars=x$p_Bronars, p_prop=x$p_com, prop="Proposition 3")) %>%
  bind_rows()
p4s <- c(p4_00, p4_05, p4_10, p4_15, p4_20) %>%
  keep(function(x) x$id %in% symmetric$id) %>%
  map_df(function(x) tibble(p_bronars=x$p_Bronars, p_prop=x$p_com, prop="Proposition 4")) %>%
  bind_rows()
p3s %>% bind_rows(p4s) %>% 
  ggplot(aes(x=p_prop, y= (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) +
  geom_histogram(binwidth=0.05, boundary=0) +
  theme_bw() +
  facet_grid(prop ~ p_bronars) +
  labs(x = "p-value",
    caption="Distribution of p-values for main propositions under different probabability of random (Bronars) choices.\nHistogram bars are 0.05 wide.",
       y = "Fraction") +
  scale_x_continuous(breaks=c(0,0.5,1))
ggsave(here("graphs", "power_analysis.pdf"), width=7, height=5, units="in")

```

