---
title: "Testing rationality"
author: "Erik Ø. Sørensen"
date: '`r format(Sys.time(), "%d %B, %Y")`'
html_document:
  keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(targets)
library(revealedPrefs)
tar_load(mmzame_decisions, store = here::here("_targets"))
tar_load(pure_bronars, store = here::here("_targets"))

```


# CCEI for the empirical data
We are interested in Afriat's cost efficiency index for each of the treatments.

First, recoding to final treatment names, then calculating CCEI's for each 
individual/treatment combination.
```{r}
mmzame_decisions <- mmzame_decisions %>% 
  mutate(treatment = fct_recode(factor(treatment, levels=c("dictator","risk","moral")),
                                "Social Choice" = "dictator",
                                "Social Risk" = "moral",
                                "Personal Risk" = "risk"))
cceis <- c()
domains <- c()
ids <- c()
for (i in unique(mmzame_decisions$id)) {
  for (j in unique(mmzame_decisions$treatment)) {
    x_df <- mmzame_decisions %>% filter(id==i, treatment==j) %>% select(x,y)
    p_df <- mmzame_decisions %>% filter(id==i, treatment==j) %>% mutate(px=maxy/maxx, py = 1) %>% select(px,py)
    ids <- c(ids, i)
    cceis <- c(cceis, ccei(x_df,p_df))
    domains <- c(domains, j)
  }
}
ccei_df <- tibble(id=ids, 
                  ccei=cceis, 
                  domain=factor(domains, levels=c("Social Choice", "Personal Risk","Social Risk")))
```

Now, some descriptive statics on these CCEIs:
```{r}
ccei_df %>% group_by(domain) %>%
  summarize( mean_ccei = mean(ccei),
             above_90 = mean( ccei>0.9)) %>%
  gt::gt() |> gt::fmt_number(decimals=3)
```

For the people we use in table 4:
```{r}
ccei_df |> filter(id %in% c(511,635,317,645)) |> gt::gt() |> gt::fmt_number(decimals=3, columns=2)
```

The average distribution of min and max CCEI (of the Social Risk and Private Risk).

```{r}
ccei_df |> filter(domain != "Social Choice") |>
  group_by(id) |>
  summarize(minCCEI = min(ccei),
            maxCCEI = max(ccei)) |>
  summarize(mean_minCCEI = mean(minCCEI),
            mean_maxCCEI = mean(maxCCEI))
```



## CCEI - distribution by domain
Now we want to cut the CCEIs into groups and plot grouped bar charts
to show the distribution.

```{r}
ccei_bar_data <- ccei_df %>% mutate(ccei_group = cut_width(ccei, 0.10, boundary=1, closed="right"))
ccei_bar_fractions <- ccei_bar_data %>%
  group_by(domain, ccei_group) %>% 
  tally() %>%  
  ungroup() %>%
  complete(domain,ccei_group, fill=list(n=0)) %>%
  group_by(domain) %>%
  mutate( fraction = n/sum(n))
```


```{r}
ccei_bar_fractions %>% ggplot(aes(x=ccei_group, y=fraction, group=domain, fill=domain)) + 
  geom_bar(stat="identity", position=position_dodge2()) +
  labs(x = "CCEI",
       y = "Fraction of subjects") +
  theme_minimal() + 
  theme(legend.title=element_blank()) + 
  scale_fill_grey() + 
  scale_y_continuous(limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1.0))
ggsave(here::here("graphs","empirical_cceis.pdf"), width=16, height = 10, units = "cm")
```




# Bronars data output

I have pre-calculated the Bronars numbers, and summarize these:
```{r}
bronars_df <- tibble(domain = "Bronars", ccei=pure_bronars)
bronars_df %>% summarize(Bronars_mean_ccei = mean(ccei),
                         Bronars_above_90 = mean( ccei>0.9)) %>%
  gt::gt() |>
  gt::fmt_number(decimals=3)
```

I append the Bronars data to the actual CCEIs to create a bar chart.

```{r}
df <- ccei_df %>% mutate(domain = as.character(domain)) %>%
  group_by(id) %>% 
  summarize(min_ccei = min(ccei), 
            max_ccei = max(ccei)) %>%
  pivot_longer(min_ccei:max_ccei, names_to = "domain", values_to = "ccei") %>%
  bind_rows(bronars_df) %>%
  mutate(outcome = fct_recode( factor(domain, levels=c("min_ccei", 
                                          "max_ccei", 
                                          "Bronars")),
                               "Empirical minimum" = "min_ccei",
                               "Empirical maximum" = "max_ccei",
                               "Simulated (Bronars)" = "Bronars")) %>%
  mutate(ccei_group = cut_width(ccei, 0.10, boundary=1, closed="right")) %>%
  group_by(outcome, ccei_group) %>% 
  tally() %>%  
  ungroup() %>%
  complete(outcome, ccei_group, fill=list(n=0)) %>%
  group_by(outcome) %>%
  mutate( fraction = n/sum(n))
``` 

Having calculated the numbers to be shown, what remains is to plot the bar chart:
```{r}
df %>% ggplot(aes(x=ccei_group, y=fraction, group=outcome, fill=outcome)) +
  geom_bar(stat = "identity", position=position_dodge2()) +
  labs(x = "CCEI",
       y = "Fraction of subjects") +
  theme_minimal() + 
  theme(legend.title=element_blank()) + 
  scale_fill_grey() +
  scale_y_continuous(limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1.0))
ggsave(here::here("graphs", "empirical_cceis_and_Bronars.pdf"), width=16, height = 10, units="cm")
```

```{r}
df |> filter(ccei_group == "(0.9,1]")
```

